Modelling the emergence of whisker barrels

### 2020-06-19 paper/briefpaper/brief.tex
resolved conflict

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin,

@@

A cortical boundary enclosing 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.
%
\mpfour{The signalling gradients are assumed not to interact with the barrel
  field boundary and to continue well beyond its extent (see
  \citealp{miller_epha7-ephrin-a5_2006}, their Fig.\,11) in order to
  participate in other developmental processes, such as inter-area positional
  specification \citep{sur_patterning_2005,oleary_area_2007}.} % Just oleary_area_2007 would be ok
%
From
>>>>>>> 7ffae6aecb56153dad7c6dd9a5aa658a6d9e293d
random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the selectivity of the connection density, $\mu(\mb{x},t)$. We summed this measure
  across the entire barrel domain and named it $\omega(t)$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the selectivity measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}

>>>>

The only differences between thalamic projections are their strengths of
interaction with the guidance fields, $\gamma$, hence any reliable differences
between emergent cortical fields must be due to differences in these values
only. We speculate that the contribution of a given ephrin field, to the
velocity at which a projection migrates across the cortical subplate, is
determined by the concentration of a similar molecule at its thalamic origin,\stu{We concentrate on the representation of the 41 macrovibrissae because their thalamic and cortical correlates are easily identifiable and consistently positioned, we exclude the microvibrissae to limit the complexity of the simulations, and we exclude the five rhinal whiskers as their representation in S1 is isolated from the main barrel field.} A cortical boundary enclosing \stu{the} 41 \cmnt{macrovibrissae} barrels was traced from
a cytochrome oxidase stain from \cite{zheng_signal_2001} \cmnt{(using the
  authors' original data)}, and Eqs.~\ref{eq:dc}--\ref{eq:comp} were solved
for $N=41$ projections on the resulting domain, using $M=2$ linear signalling
gradients aligned with the anterior-posterior and medial-lateral axes.

@@

\mpfour{The signalling gradients are assumed not to interact with the barrel
  field boundary and to continue well beyond its extent (see
  \citealp{miller_epha7-ephrin-a5_2006}, their Fig.\,11) in order to
  participate in other developmental processes, such as inter-area positional
  specification \citep{sur_patterning_2005,oleary_area_2007}.} % Just oleary_area_2007 would be ok
%
From random initial conditions for $a(\mb{x},0)$, \cmnt{with each hexagonal element
  of $a_i$ set from a uniform distribution according to $0.2+{U}(0,0.2)$, and
  $c(\mb{x},0)=0$}, a clear Voronoi-like tesselation
emerged (Fig.\,\ref{fig:main}C; see Movie S1). A reduction in the Honda delta
metric (see \citealp{senft_mouse_1991}) confirmed that a `good' Voronoi
pattern emerged within \cmnt{$\approx$~20000} iterations
(Fig.\,\ref{fig:main}D).  A measure of the difference in \cmnt{barrel area}
between real and simulated barrels revealed a strong correspondence (see
Fig.\,\ref{fig:main}D, squares). \cmnt{In a chosen region, the ratio of
  \emph{the connection density of the TC type $i$ which makes the densest
    connections} to \emph{the sum of all connection densities} gives a measure
  of the selectivity of the connection density, $\mu(\mb{x},t)$. We summed this measure
  across the entire barrel domain and named it $\omega(t)$ (see
  Fig.\,\ref{fig:main}D, grey hexagons). $\omega$ increases during the first
  20000 simulation steps and converges on a stable
  value. Fig.\,\ref{fig:main}E shows the selectivity measure plotted as a
  luminance map, giving a more graded impression of the structure which
  develops in the system.}
